MixEth: efficient trustless coin mixing service for Ethereum

### 2018-10-23 article/main.tex
Challenging transaction in article updated

\section{Background}
\subsection{Notations}
In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK$ denote the set of public keys belonging to receivers.

@@

$0\lor1\leftarrow 
ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving two Chaum-Pedersen zero-knowledge proofs that the following two tuples are DDH-tuples: $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i-1})$ and $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i})$. If both of the proof verifies and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected. These proofs and checks allow one to check that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.

@@

\subsection{Withdrawing}
Let $C^*$ be the final shuffling accumulated constant. For a recipient whose public key $sG \in initPubKeys[]$, in the final shuffle there will be $sC^*$. The recipient can prove to MixEth that she knows $s$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
\subsection{MixEth pseudocode}

>>>>

\section{Background}
\subsection{Notations}
In most cases if it is possible we will stick to the notations used in \cite{meiklejohn2018mobius} for sake of uniformity. 
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK_{i}$ denote the set of public keys belonging to receivers at a particular shuffling round $i$.

@@

$0\lor1\leftarrow 
ChallengeShuffle(PK_{i},C^{*}_{i},PK_{i-1},C^{*}_{i-1},pk_{B})$: receiver $B$ with public key $pk_{B}=s_{B}G$ can challenge an incorrect shuffle at the $i$th round by giving two Chaum-Pedersen zero-knowledge proofs that the following two tuples are DDH-tuples: $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i-1})$ and $(G, s_{B}G, C^{*}_{i-1}, s_{B}C^{*}_{i})$. If both of the proofs are verified and $s_{B}C^{*}_{i} \notin PK_{i}$, while $s_{B}C^{*}_{i-1} \in PK_{i-1}$, then the challenge is accepted, otherwise rejected. These proofs and checks allow one to check that indeed the $i$th round is the first round in which the corresponding public key to $s_{B}$ is shuffled incorrectly.

@@

We also highlight the necessity of two Chaum-Pedersen proofs for challenging a shuffle. If only one Chaum-Pedersen proof is enclosed in the challenging transaction, MixEth can not be sure that the integrity of the problematic public key indeed in the $i$th shuffling round was compromised. This could be abused by a malicious shuffler who deliberately corrupts their own public key in their shuffling round and afterwards they could blame any other shuffler for the compromise. This could have been led to losses of honest recipients' deposit.

\subsection{Withdrawing}
Let $C^*$ be the final shuffling accumulated constant. For a recipient $B$, whose public key $s_{B}G \in initPubKeys[]$, in the final shuffle there will be $s_{B}C^*$. The recipient can prove to MixEth that she knows secret key $s_{B}$ by using a modified ECDSA, which uses $C^*$ as the generator element instead of the standardized $G$.
\subsection{MixEth pseudocode}
